Analyzing Security-Cost Trade-off for a \\ Fully Homomorphic Encryption Scheme

### 2013-06-16 Report/article.tex
figures

\section{Conclusion}
With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity. The experiments with the implementation 
\pagebreak

>>>>

\section{Conclusion}

With the examples and the programs discussed, we conclude that the tranformation of a non-straight line programs(with branching) in general increases the circuit complexity. The experiments on the implementation and the operations ........
\pagebreak
